Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-03-07 manuscript.Rmd
classification description

## Data Sharing and Transparency

<!-- WHAT CAN WE SHARE AND HOW -->

>>>>

Windowed datasets were used for machine learning classification and validation. For each analysis reported in the results, a subset of data were defined as a "training" set and another, independent portion of the data were defined as a "testing" set. Different training/testing set combinations were used to address different goals; here we describe the general procedure of how a classifier was derived from a training set. Random forest models [@Breiman2001] were trained to predict the human coded body position label for each window from the set of 436 motion features using the *randomForest* package in R [@LiawWiener2002]. Random forest models use random subsets of features and random subsets of data across many iterations; this random subsetting creates models that are less likely to be overfit. The *tidymodels* set of packages in R was used to tune the "mtry" and "ntrees" hyperparameters, which control the number of columns used and the total number of trees created when modeling. We use an mtry parameter of 44 and and ntree parameter of 550, however, changing hyperparameters had little impact on model performance. Just like a linear regression model, the resulting random forest model could later be applied to a set of testing data with the *predict* function. Validation analyses below will compare the human-coded annotations and random forest model predictions for testing data that are independent from training data, providing a test of whether models can successfully generalize.
<!-- cite tidymodels -->

<!-- ## Data Sharing and Transparency -->
<!-- WHAT CAN WE SHARE AND HOW -->
